### 2014-03-16 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:16	19:56:37	(Sun16.Mar)

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as we use subarray averaging mainly to deal with the coherent echoes in active sonar. We have now stated this better up front in the article.}

@@

\ai{Thank you for this remark. We agree fully, and will state this better up front in the abstract. TODO}

>>>>

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as to the best of our knowledge this term is usually used to describe the use of subarrays to reduce complexity, while we average over subarrays to deal with the coherent echoes present in \emph{active} systems. We still apply the weights to the full array. To avoid confusion we have now stated this better up front in the article.}

@@

\ai{We agree with the reviewer that this should be improved. We still state the two order of magnitude improvement over our reference implementation as this is the total improvement we obtained, but also state that this figure would likely be 5-10 had a similar effort been carried out on the CPU side as well.}
